---
title: "gephi-ready-csv"
author: "Dre Dyson"
date: "4/5/2021"
output: html_document
---

# Introduction
This R Package will allow you to generate a GEPHI ready CSV file. GEPHI is a Free and Open Source network visualization tool commonly used in Academia. GEPHI allows you to explore, manipulate, and represent various techniques in Network Analysis. 

---

#### This Document will illustrate the process of creating the GEPHI ready file in the following steps:
 + Data Mining with Twitter with R Package 'rtweet'
 + Data Manipulate with popular R Package 'dplyr'
 + Visualize Raw Tweets
 + Creation on R Package Function

---


```{r packages}
library("rtweet",warn.conflicts = F)
library("dplyr",warn.conflicts = F)
library("readr",warn.conflicts = F)
library("ggplot2",warn.conflicts = F)
library("data.table",warn.conflicts = F)
options(scipen = 9999)

```


```{r proof_of_work, eval = F}
#### Data Mining ####
#### 
# Find English only Tweets relating to the 2021 Derek Chauvin Trial

tweets <- rtweet::search_tweets(q = "derek chauvin trial", 
                                n = 18000,
                                include_rts = T,
                                lang = "en")
# readr::write_excel_csv(tweets, "rtweet_output.csv")
# End Find English only Tweets relating to the 2021 Derek Chauvin Trial


```



#### We are running this on my local computer. For the sake of the RMarkdown file, we save rTweet's output file. This helps with not having to re-run Twitter's API calls.



```{r local_machine}
tweets <- data.table::fread("/Users/dre/Downloads/module12/rtweet_output.csv")
```


#### Simple Data manipulation with dplyr


```{r data_manipulation}
#### DATA Manipulation ####
#### 
# Filter only records with RTs
tweets_rts <- tweets %>% select(screen_name, retweet_name)
tweets_rts <- tweets_rts %>% filter(!is.na(retweet_name))
# End Filter only records with RTs


# Change user_names to factors 
tweets_rts <- tweets_rts %>% mutate(screen_name = as.factor(screen_name),
                             retweet_screen_name = as.factor(retweet_name))
# End Change user_names to factors 


# Create Adjacency list with weight (n)
twitter_adjacency <- tweets_rts %>% group_by(screen_name, retweet_name) %>% tally()  %>% arrange(desc(n))
colnames(twitter_adjacency) <- c("Target", "Source", "Weight")

twitter_adjacency <- twitter_adjacency %>% mutate(Type = "Undirected")
# End Create adjacency list
# 
```


#### Lets check out the output

```{r output}
head(twitter_adjacency)
```

#### Now lets create a simple Time Series Chart with the frequency of Tweets.


```{r vis}
rtweet::ts_plot(data = tweets, by = "hours") +
  xlab("Date") +
  ylab("Freq of Tweets")


```


#### This is the function I created so an user can supply their Twitter API information, along with the search query and number of tweets. \n
See vignette("auth", package = "rtweet") for more information about obtaining a Twitter API


```{r create_function, eval=F}
twitter_gephi_file <- function(query, num_tweets,language, twitter_api_key, twitter_api_secret, app_name){
  # Twitter Auth -- To see more visit vignette("auth", package = "rtweet")
  api_key <- twitter_api_key
  
  api_secret_key <- twitter_api_secret
  
  token <- rtweet::create_token(app = app_name,
                                consumer_key = api_key,
                                consumer_secret = api_secret_key)
  
  tweets <- rtweet::search_tweets(q = query, 
                                  n = num_tweets,
                                  include_rts = T,
                                  lang = language,
                                  token = token)
  # End Twitter Auth
  
  # Create adjacency list
  tweets_rts <- tweets %>% dplyr::select(screen_name, retweet_screen_name)
  
  tweets_rts <- tweets_rts %>% dplyr::filter(!is.na(retweet_screen_name))
  
  tweets_rts <- tweets_rts %>% dplyr::mutate(screen_name = as.factor(screen_name),
                             retweet_screen_name = as.factor(retweet_screen_name))
  
  twitter_adjacency <- tweets_rts %>% dplyr::group_by(screen_name, retweet_screen_name) %>% 
    tally() %>% 
    arrange(desc(n))
  
  colnames(twitter_adjacency) <- c("Target", "Source", "Weight")
  twitter_adjacency <- twitter_adjacency %>% dplyr::mutate(Type = "Directed")
  # End adjacency list
  return(twitter_adjacency)
}

```

NOT RUN
```{r run_function, eval=F}
twitter_network <- twitter_gephi_file(query = "derek chauvin trial",
                                      num_tweets = 18000,
                                      language = "en", 
                                      twitter_api_key = "XXXXXXXX",
                                      twitter_api_secret = "XXXXXXX",
                                      app_name = "XXXXX")

```